### 2022-04-19 greta/hopf_decrease_mcmc.Rmd
some mcmc work

```{r}
t_max <- train_t_max + test_t_max
sim <- purrr::map_dfr(1:train_reps, \(i) simulate(t_max=t_max, delta=-0.1, Ko=30), .id = "i")
train <- sim |> filter(t <= train_t_max)
test <- sim |> filter(t > train_t_max)
# test <- purrr::map_dfr(1:test_reps, \(i) simulate(t_max=test_t_max), .id = "i")

>>>>

```{r}
t_max <- train_t_max + test_t_max
sim <- purrr::map_dfr(1:train_reps, \(i) simulate(t_max=t_max, delta=-0.08, Ko=30), .id = "i")
train <- sim |> filter(t <= train_t_max)
test <- sim |> filter(t > train_t_max)
# test <- purrr::map_dfr(1:test_reps, \(i) simulate(t_max=test_t_max), .id = "i")

### 2022-04-19 greta/stochastic_mcmc.Rmd
some mcmc work

set.seed(4242)
train_reps <- 10
train_t_max <- 250
test_t_max <- 250
test_reps <- 1000

@@

```{r}
# View the bistable curve: 
# curve( (0.75 - x)**2 * (0.25 - x), 0, 1)

step <- function(N, eta,  a = 0.75, b = 0.25) {
  N <- N + (a - N)**2 * (b - N) + eta
  N <- np.clip(N, 0, 1)
  N
}

# simulate
simulate <- function(N_init = 0.75,
                     t_max = 250L,
                     mu =0, # -5e-4,
                     sigma = 1e-2,
                     a = 0.75, 
                     b = 0.25) {
  eta <- rnorm(t_max, mu, sigma)
  N   <- numeric(t_max)
  N[1] <- N_init
  for (t in 1:(t_max-1)) {
    N[t+1] <- step(N[t], eta[t], a = a, b = b)
  }
  tibble::tibble(t = 1:t_max, N = N)
}

@@

posterior_samples <- 
  bind_rows(map(draws, as_tibble)) %>% 
  sample_n(test_reps)
posterior_sims <- posterior_samples %>%
  purrr::transpose() %>%
  map_dfr(function(q) simulate(t_max = test_t_max) ,.id = "i")

bind_rows(test, posterior_sims, .id = "model")|> 
  ggplot(aes(t, N, col=model, group=interaction(model,i))) +
           geom_line(alpha=0.1)

@@

```{r}
true <- tibble(a = 0.75, b = 0.25, sigma = 1e-2) |> gather(variable, value)

posterior_samples  |> gather(variable, value) |> ggplot() + 
  geom_histogram(aes(value), bins = 30)  +
  geom_vline(data = true, aes(xintercept = value), col = "red", lwd = 1) + 
  facet_wrap(~variable, scales = "free")
```

>>>>

set.seed(4242)
train_reps <- 100
train_t_max <- 250
test_t_max <- 250
test_reps <- 100

@@

```{r}
# View the bistable curve: 
#curve( (0.75 - x)**2 * (0.25 - x), 0.749999, 0.750001)
#curve(0*x,0,1,add = TRUE)

#curve((0.25 - x)**2 * (0.75 - x), 0, 1)
#curve(0*x,0,1,add = TRUE)
```

```{r}
step <- function(N, eta,  a = 0.75, b = 0.25) {
  N <- N + (a - N)**2 * (b - N) + eta
  N <- np.clip(N, 0, 1)
  N
}

# simulate
simulate <- function(N_init = 0.75,
                     t_max = 1250L,
                       p = list(
                       sigma = 1e-2,
                       a = 0.75, 
                       b = 0.25)) {
  eta <- rnorm(t_max, 0, p$sigma) # mu = 0, no drift
  N   <- numeric(t_max)
  N[1] <- N_init
  for (t in 1:(t_max-1)) {
    N[t+1] <- step(N[t], eta[t], a = p$a, b = p$b)
  }
  tibble::tibble(t = 1:t_max, N = N)
}

@@

posterior_samples <- 
  bind_rows(map(draws, as_tibble)) %>% 
  sample_n(test_reps)
posterior_sims <- posterior_samples %>%
  purrr::transpose() %>%
  map_dfr(function(q) simulate(t_max = test_t_max, p = q) ,.id = "i")

bind_rows(
  mutate(test, model="true"), 
  mutate(posterior_sims, model="predicted")
)|> 
  ggplot(aes(t, N, col=model, group=interaction(model,i))) +
           geom_line(alpha=0.1)

@@

```{r}
true <- tibble(a = 0.75, b = 0.25, sigma = 1e-2) |> gather(variable, value)
bind_rows(map(draws, as_tibble)) |>
  gather(variable, value) |> ggplot() + 
  geom_histogram(aes(value), bins = 30)  +
  geom_vline(data = true, aes(xintercept = value), col = "red", lwd = 1) + 
  facet_wrap(~variable, scales = "free")
```
